---
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
FlixGem <- read_csv(here("/Users/zhizhiwei/Downloads/Final_Project_FlixGem.csv"))
```

&nbsp;

## Task 3:

### Clean data again (only drop NAs for directors, Hidden gem score and title):
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=80)}
FlixGem_cleaned_task3 <- FlixGem %>% filter(`Series or Movie`== "Movie") %>% drop_na(Director,`Hidden Gem Score`,Title)
```

&nbsp;

### Select Directors, Movie title and HG-score out:
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=80)}
FlixGem_cleaned_HG <- FlixGem_cleaned_task3 %>% group_by(Director,Title) %>% select(Director,Title,`Hidden Gem Score`) %>% arrange(Director)
```

&nbsp;

### Split a list for each director:
```{r}
FlixGem_cleaned_HG_split <- with(FlixGem_cleaned_HG, split(FlixGem_cleaned_HG,Director))
```

```{r}
length(FlixGem_cleaned_HG_split)
```

&nbsp;

### Function that takes in a director's list and return his/her HG-H index:
```{r}
calculate_HG_H_for_sapply <- function(each_director_list){
    H <- 0
    for(i in seq_along(each_director_list$`Hidden Gem Score`)){
      if(each_director_list$`Hidden Gem Score`[i]>=i){
        H<-H+1
      }
    }
    return(H)
}
```

&nbsp;

### Apply the function to the splitted list and returns the vector containing HG-H scores for all directors:
```{r}
HG_H_index_vec <-sapply(FlixGem_cleaned_HG_split, calculate_HG_H_for_sapply)
```

&nbsp;

### Convert the vector to a tibble:
```{r}
all_HG_H_index <-as.tibble(HG_H_index_vec)
```

&nbsp;

### Combine the Director names and their HG-H scores into one tibble:
```{r}
Director_name_tibble <- FlixGem_cleaned_HG[,1] %>% unique(.)

combined_name_H_index <- bind_cols(Director_name_tibble, all_HG_H_index)
```


&nbsp;

### Find the top 10 directors according to their HG-H index:
```{r}
top_10 <- combined_name_H_index %>% arrange(desc(value)) %>% head(10)
colnames(top_10) <- c("Director","HG-H-index")
top_10
```

